Preserving Reciprocal Consistency in Distributed Graph Databases

### 2020-04-06 paper/figures/reciprocally-consistent-edge.tex
rename tikz node+

\begin{figure}[ht!]
  \centering
  \begin{tikzpicture}[node distance=2cm]
    \node (v1) [vertex2,xshift=0cm,yshift=0cm] {\small{\texttt{a:\textcolor{green}{Person}}}};

    \node (v2) [vertex2,xshift=5cm,yshift=0cm] {\small{\texttt{b:\textcolor{green}{Book}}}};

>>>>

\begin{figure}[ht!]
  \centering
  \begin{tikzpicture}[node distance=2cm]
    \node (v1) [big_vertex,xshift=0cm,yshift=0cm] {\small{\texttt{a:\textcolor{green}{Person}}}};

    \node (v2) [big_vertex,xshift=5cm,yshift=0cm] {\small{\texttt{b:\textcolor{green}{Book}}}};
